Chronic imaging of cortical oxygen tension and blood flow after targeted vascular occlusion

### 2018-04-25 article.tex
Fixed inconsistency in scale bar description in caption
Dropped generation of the table list
There are no tables in this document
Added address for Institute of Neuroscience
Based on Taylor’s review

\author[a]{Colin T. Sullender}
\author[a]{Andrew E. Mark}
\author[b,c]{Taylor A. Clark}
\author[d]{Tatiana V. Esipova}
\author[d]{Sergei A. Vinogradov}
\author[b,c]{Theresa A. Jones}
\author[a,c*]{Andrew K. Dunn}
\affil[a]{The University of Texas at Austin, Department of Biomedical Engineering, 107 W. Dean Keeton St. Stop C0800, Austin, TX, 78712, USA}
\affil[b]{The University of Texas at Austin, Department of Psychology, 108 W. Dean Keeton St. Stop A8000, Austin, TX, 78712, USA}
\affil[c]{The University of Texas at Austin, Institute for Neuroscience, Austin, Texas 78712, USA}
\affil[d]{University of Pennsylvania, Department of Biochemistry and Biophysics, Philadelphia, PA, 19104, USA}

@@

% Figure 3 - Static Oxygen Tension
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure3.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:static_oxygen}
        All scale bars = 1 mm. (a) Speckle contrast image of cortical flow overlaid with regions targeted for \pO\ measurements. Two descending arterioles (A1, A2), two veins (V1, V2), and one parenchyma region (P1) were examined. The projected patterns ranged between 0.014 - 0.046 mm$^2$ in area. (b) \pO\ measurements within the targeted regions conducted using both 445 nm and 637 nm excitation of Oxyphor PtG4 (mean $\pm$ s.d.). (c) 445 nm and (d) 637 nm \pO\ maps produced using tiled excitation patterns covering a 1.2 x 1.0 mm area. Each individual tile has a projected area of 0.012 mm$^2$.
    }
\end{figure}

@@

% ----------------------------------------------------------------------------------------
% FIGURE AND TABLE LISTS
% ----------------------------------------------------------------------------------------
\listoffigures
\listoftables

>>>>

\author[a]{Colin T. Sullender}
\author[a]{Andrew E. Mark}
\author[b,c]{Taylor A. Clark}
\author[d]{Tatiana V. Esipova}
\author[d]{Sergei A. Vinogradov}
\author[b,c]{Theresa A. Jones}
\author[a,c*]{Andrew K. Dunn}
\affil[a]{The University of Texas at Austin, Department of Biomedical Engineering, 107 W. Dean Keeton St. Stop C0800, Austin, TX, 78712, USA}
\affil[b]{The University of Texas at Austin, Department of Psychology, 108 W. Dean Keeton St. Stop A8000, Austin, TX, 78712, USA}
\affil[c]{The University of Texas at Austin, Institute for Neuroscience, 1 University Station Stop C7000, Austin, Texas 78712, USA}
\affil[d]{University of Pennsylvania, Department of Biochemistry and Biophysics, Philadelphia, PA, 19104, USA}

@@

% Figure 3 - Static Oxygen Tension
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure3.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:static_oxygen}
        Scale bars = 1 mm. (a) Speckle contrast image of cortical flow overlaid with regions targeted for \pO\ measurements. Two descending arterioles (A1, A2), two veins (V1, V2), and one parenchyma region (P1) were examined. The projected patterns ranged between 0.014 - 0.046 mm$^2$ in area. (b) \pO\ measurements within the targeted regions conducted using both 445 nm and 637 nm excitation of Oxyphor PtG4 (mean $\pm$ s.d.). (c) 445 nm and (d) 637 nm \pO\ maps produced using tiled excitation patterns covering a 1.2 x 1.0 mm area. Each individual tile has a projected area of 0.012 mm$^2$.
    }
\end{figure}

@@

% ----------------------------------------------------------------------------------------
% FIGURE AND TABLE LISTS
% ----------------------------------------------------------------------------------------
\listoffigures
